---
title: "Adding Overdose Columns From ICD-9-CM and ICD-10-CM"
author: epinotes
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: paper
    source_code: embed
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(DT)
library(tidyverse)

# source relevant functions from github

source("https://raw.githubusercontent.com/injuryepi/overdoser/master/R/od_drug_apr_icd9cm.R")

source("https://raw.githubusercontent.com/epinotes/useicd10cm/master/R/icd_drug_opioid.R")

source("https://raw.githubusercontent.com/injuryepi/overdoser/master/R/od_create_diag_9.R")

source("https://raw.githubusercontent.com/epinotes/useicd10cm/master/R/icd_new_diag.R")

```

ICD-10-CM
=====================================    

Inputs {.sidebar}
-----------------------------------------------------------------------

</br>

To select multiple variables, click on each variable you want to include. To remove a variable already selected, click on the variable then hit backspace.  

</br>

```{r}

fileInput('file10', 'Find the CSV file with ICD-10-CM',
                  accept=c('text/csv', '.csv'))


selectizeInput('ediag10', 'Diagnosis and Ecode fields', choices = NULL, multiple = TRUE)

selectizeInput('uid10', 'Unique ID', choices = NULL, multiple = F)

# Download Button

actionButton("submit", "Submit")


```


Row {data-height = 1000}
-----------------------------------------------------------------------

### Preview The New Data Output With The Additional OD Variables


```{r}

hosp_data10 <- reactive({

      infile10 <- input$file10

      req(infile10)

      read_csv(infile10$datapath)

    })


```



```{r}
observeEvent(input$file10,{
 updateSelectizeInput(session, 'ediag10', choices = names(hosp_data10()))
 })

```


```{r}
observeEvent(input$file10,{
 updateSelectizeInput(session, 'uid10', choices = names(hosp_data10()))
 })

```


```{r}

outputdata10 <- 
reactive(if(!is.null(input$ediag10) && !is.null(input$uid)){
  sel10 = unique(unlist(list(strsplit(input$ediag10,","), strsplit(input$uid10,","))))
                hosp_data10() %>% 
                  select(!!sel10, everything())
                })


```

```{r}

dxm10 <- reactive(1:(ncol(outputdata10())-1))


outputdata10_2 <- eventReactive(input$submit, {outputdata10() %>%
	  icd_drug_opioid(., diag_ecode_col = dxm10())})

reactive(outputdata10_2())

```

Row {data-height = 10}
------------------------------

### Download The New File

```{r}

p(downloadButton("download10", "Download file", class = "btn-primary"))

```

```{r}
# Downloadable csv of the new file
  output$download10 <- downloadHandler(
    filename = function() {
      paste0("new_", input$file10)
    },
    content = function(file) {
      write_csv(outputdata10_2(), file)
    }
  )

```



ICD-9-CM
=====================================  
Inputs {.sidebar}
-----------------------------------------------------------------------


</br>

For each variable you can select (click) or remove(backspace) multiple values.

</br>

```{r}

fileInput('file9', 'Find the CSV file with ICD-9-CM',
                  accept=c('text/csv', '.csv'))

selectizeInput('diag1', 'Principal Diagnosis', choices = NULL, multiple = F)

selectizeInput('ediag', 'Diagnosis and Ecode fields', choices = NULL, multiple = TRUE)

selectizeInput('uid', 'Unique ID', choices = NULL, multiple = F)

# Download Button

actionButton("go", "Submit")


```


Row {data-height = 1000}
-----------------------------------------------------------------------

### Preview The New Data Output With The Additional OD Variables


```{r}

hosp_data <- reactive({

      infile <- input$file9

      req(infile)

      read_csv(infile$datapath)

    })


```



```{r}
observeEvent(input$file9,{
  updateSelectizeInput(session, 'diag1', choices = names(hosp_data()))
  
})

```

```{r}
observeEvent(input$file9,{
 updateSelectizeInput(session, 'ediag', choices = names(hosp_data()))
 })

```


```{r}
observeEvent(input$file9,{
 updateSelectizeInput(session, 'uid', choices = names(hosp_data()))
 })

```


```{r}

outputdata <- 
reactive(if(!is.null(input$diag1) && !is.null(input$ediag) && !is.null(input$uid)){ 
  sel9 = unique(unlist(list(strsplit(input$diag1,","), strsplit(input$ediag,","), strsplit(input$uid,","))))
                hosp_data() %>% 
                  select(!!sel9, everything())
                })



```


```{r}

dxm <- reactive(2:(ncol(outputdata())-1))


outputdata2 <- eventReactive(input$go, {outputdata() %>% 
	  od_drug_apr_icd9cm(., diag_col = 1, ecode_col = dxm())})


reactive(outputdata2())

```


Row {data-height = 10}
------------------------------

### Download The New File

```{r}

p(downloadButton("download", "Download file", class = "btn-primary"))

```

```{r}
# Downloadable csv of selected dataset ----
  output$download <- downloadHandler(
    filename = function() {
      paste0("new_", input$file9)
    },
    content = function(file) {
      write_csv(outputdata2(), file)
    }
  )

```

README
=====================================   

</br>

</br>

<h5 style='color:darkblue;font-weight:bold;background-color:yellow'> This shiny application was designed for testing and proof of concept, not for uploading confidential data. You can build and use the application locally.
</h5>

</br>

<H4> Uploading files </H4>  

You need only to upload the diagnosis and E-code fields of your dataset, and a unique ID field to ease joining back the newly coded file to its source file. Before uploading the file into the shiny app, separate the dataset with ICD-9-CM from the dataset with ICD-10-CM. In addition the unique ID can be anonymized using methods provided by the R package [anonymizer](https://github.com/paulhendricks/anonymizer).
 You can file any issue at the github page or email __epinotes@gmail.com__

<H4> Source Codes </H4>  

1. Find the source rmarkdown code of this document at [GitHub](https://github.com/injuryepi/shiny_utils/blob/master/upload_file_for_OD_coding.Rmd)  

2. The main R functions for coding the drug overdoses are:  

- [od_drug_apr_icd9cm()](https://github.com/injuryepi/overdoser/blob/master/R/od_drug_apr_icd9cm.R) 

- [od_create_diag_9()](https://github.com/injuryepi/overdoser/blob/master/R/od_create_diag_9.R)  

- [icd_new_diag()](https://github.com/epinotes/useicd10cm/blob/master/R/icd_new_diag.R)  

- [icd_drug_opioid()](https://github.com/epinotes/useicd10cm/blob/master/R/icd_drug_opioid.R) 

<H4> Overdose Definitions </H4>  

1. ICD-9-CM   

- __All drug__: Principal diagnosis of _960-979_   
OR any E-code of _E850-E858, E950.0-E950.5, E962.0, E980.0-E980.5_  

- __Heroin__: Principal diagnosis of _965.01_   
OR any E-code _E850.0_    

- __Non-Heroin Opioid__: Principal diagnosis of _965.00, 965.02, 965.09_   
OR any E-code of _E850.1, E850.2_      
Then exclude any cases of heroin as defined above.      


2. ICD-10-CM    

- __All drug__: Any diagnosis of _T36-T50_  
AND a 6th character of _1,2,3, or 4_ for _T36.9, T37.9, T39.9, T41.4, T42.7, T43.9, T45.9, T47.9, and T49.9_, or a 5th character of _1,2,3, or 4_ for all the others _T36-T50_  
AND a 7th character of _A or missing_  

- __Heroin__: Any diagnosis of _T40.1X_  
AND a 6th character of _1,2,3, or 4_  
AND a 7th character of _A or missing_

- __Non-Heroin Opioid__: Any diagnosis of _T40.0X, T40.2X, T40.3X, T40.4X,T40.60, T40.69_  
AND a 6th character of _1,2,3, or 4_  
AND a 7th character of _A or missing_,  
Then exclude any cases of heroin as defined above. 

- __All Opioid__: Any diagnosis of _T40.0X, T40.1X, T40.2X, T40.3X, T40.4X, T40.60, T40.60_  
AND a 6th character of _1,2,3, or 4_  
AND a 7th character of _A or missing_

- __Stimulant__: Any diagnosis of _T40.5X, T43.60, T43.61, T43.62, T43.63, T43.64, T43.69_  
AND a 6th character of _1,2,3, or 4_  
AND a 7th character of _A or missing_







