---
title: "Adding Overdose Columns From ICD-9-CM and ICD-10-CM"
author: Mamadou Ndiaye
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: paper
    source_code: embed
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(DT)
library(tidyverse)

# source relevant functions from github

source("https://raw.githubusercontent.com/injuryepi/overdoser/master/R/od_drug_apr_icd9cm.R")

source("https://raw.githubusercontent.com/injuryepi/overdoser/master/R/od_drug_apr_icd10cm.R")

source("https://raw.githubusercontent.com/injuryepi/overdoser/master/R/od_create_diag_9.R")

source("https://raw.githubusercontent.com/injuryepi/overdoser/master/R/od_create_diag.r")

```

ICD-10-CM
=====================================    

Inputs {.sidebar}
-----------------------------------------------------------------------

</br>

To select multiple variables, click on each variable you want to include. To remove a variable already selected, click on the variable then hit backspace.  

</br>

```{r}

fileInput('file10', 'Choose CSV File',
                  accept=c('text/csv', '.csv'))


selectizeInput('ediag10', 'Diagnosis and Ecode fields', choices = NULL, multiple = TRUE)

selectizeInput('uid10', 'Unique ID', choices = NULL, multiple = F)

# Download Button

actionButton("submit", "Submit")


```


Row {data-height = 1000}
-----------------------------------------------------------------------

### New Data Output With Additional Variables


```{r}

hosp_data10 <- reactive({

      infile10 <- input$file10

      req(infile10)

      read_csv(infile10$datapath)

    })


```



```{r}
observeEvent(input$file10,{
 updateSelectizeInput(session, 'ediag10', choices = names(hosp_data10()))
 })

```


```{r}
observeEvent(input$file10,{
 updateSelectizeInput(session, 'uid10', choices = names(hosp_data10()))
 })

```


```{r}

outputdata10 <- 
reactive(if(!is.null(input$ediag10) && !is.null(input$uid)){ 
                hosp_data10()[, !duplicated(unlist(list(strsplit(input$ediag10,","), strsplit(input$uid10,",")))), drop = F]})


```

```{r}

dxm10 <- reactive(1:(ncol(outputdata10())-1))


outputdata10_2 <- eventReactive(input$submit, {outputdata10() %>%
	  od_drug_apr_icd10cm(., diag_ecode_col = dxm10())})

reactive(outputdata10_2())

```

Row {data-height = 50}
------------------------------

### Download The New File

```{r}

p(downloadButton("download10", "Download file", class = "btn-primary"))

```

```{r}
# Downloadable csv of the new file
  output$download10 <- downloadHandler(
    filename = function() {
      paste0("new_", input$file10)
    },
    content = function(file) {
      write_csv(outputdata10_2(), file)
    }
  )

```



ICD-9-CM
=====================================  
Inputs {.sidebar}
-----------------------------------------------------------------------


</br>

For each variable you can select (click) or remove(backspace) multiple values.

</br>

```{r}

fileInput('file9', 'Choose CSV File',
                  accept=c('text/csv', '.csv'))

selectizeInput('diag1', 'Principal Diagnosis', choices = NULL, multiple = F)

selectizeInput('ediag', 'Diagnosis and Ecode fields', choices = NULL, multiple = TRUE)

selectizeInput('uid', 'Unique ID', choices = NULL, multiple = F)

# Download Button

actionButton("go", "Submit")


```


Row {data-height = 1000}
-----------------------------------------------------------------------

### New Data Output With Additional Variables


```{r}

hosp_data <- reactive({

      infile <- input$file9

      req(infile)

      read_csv(infile$datapath)

    })


```



```{r}
observeEvent(input$file9,{
  updateSelectizeInput(session, 'diag1', choices = names(hosp_data()))
  
})

```

```{r}
observeEvent(input$file9,{
 updateSelectizeInput(session, 'ediag', choices = names(hosp_data()))
 })

```


```{r}
observeEvent(input$file9,{
 updateSelectizeInput(session, 'uid', choices = names(hosp_data()))
 })

```


```{r}

outputdata <- 
reactive(if(!is.null(input$diag1) && !is.null(input$ediag) && !is.null(input$uid)){ 
                hosp_data()[, !duplicated(unlist(list(strsplit(input$diag1,","), strsplit(input$ediag,","), strsplit(input$uid,",")))), drop = F]})


```


```{r}

dxm <- reactive(2:(ncol(outputdata())-1))


outputdata2 <- eventReactive(input$go, {outputdata() %>% 
	  od_drug_apr_icd9cm(., diag_col = 1, ecode_col = dxm())})

reactive(outputdata2())

```


Row {data-height = 50}
------------------------------

### Download The New File

```{r}

p(downloadButton("download", "Download file", class = "btn-primary"))

```

```{r}
# Downloadable csv of selected dataset ----
  output$download <- downloadHandler(
    filename = function() {
      paste0("new_", input$file9)
    },
    content = function(file) {
      write_csv(outputdata2(), file)
    }
  )

```

README
=====================================   

</br>

</br>

<H4> Uploading files </H4>  

You need only to upload the diagnosis and E-code fields of your dataset, and a unique ID field to ease joining back the newly coded file to its source file. Before uploading the file into the shiny app, the unique ID can be anonymized using methods provided by the R package [anonymizer](https://github.com/paulhendricks/anonymizer)

<H4> Source Codes </H4>  

1. Find the source rmarkdown code of this document at [GitHub](https://github.com/injuryepi/shiny_utils/blob/master/upload_file_for_OD_coding.Rmd)  

2. The main R functions for coding the drug overdoses are:  

- [od_drug_apr_icd9cm()](https://github.com/injuryepi/overdoser/blob/master/R/od_drug_apr_icd9cm.R) 

- [od_create_diag_9()](https://github.com/injuryepi/overdoser/blob/master/R/od_create_diag_9.R)  

- [od_create_diag()](https://github.com/injuryepi/overdoser/blob/master/R/od_create_diag.r)  

- [od_drug_apr_icd10cm()](https://github.com/injuryepi/overdoser/blob/master/R/od_drug_apr_icd10cm.R) 

<H4> Overdose Definitions </H4>  

1. ICD-9-CM   

- __All drug__: Principal diagnosis of _960-979_   
OR any E-code of _E850-E858, E950.0-E950.5, E962.0, E980.0-E980.5_  

- __Heroin__: Principal diagnosis of _965.01_   
OR any E-code _E850.0_    

- __Non-Heroin Opioid__: Principal diagnosis of _965.00, 965.02, 965.09_   
OR any E-code of _E850.1, E850.2_      
Then exclude any cases of heroin as defined above.      


2. ICD-10-CM    

- __All drug__: Any diagnosis of _T36-T50_  
AND a 6th character of _1,2,3, or 4_ for _T36.9, T37.9, T39.9, T41.4, T42.7, T43.9, T45.9, T47.9, and T49.9_, or a 5th character of _1,2,3, or 4_ for all the others _T36-T50_  
AND a 7th character of _A or missing_  

- __Heroin__: Any diagnosis of _T40.1X_  
AND a 6th character of _1,2,3, or 4_  
AND a 7th character of _A or missing_

- __Non-Heroin Opioid__: Any diagnosis of _T40.0X, T40.2X, T40.3X, T40.4X,T40.60, T40.69_  
AND a 6th character of _1,2,3, or 4_  
AND a 7th character of _A or missing_,  
Then exclude any cases of heroin as defined above.   







